
\subsection{}

Describe geometrically the sets of points z in the complex plane defined by the following relations:

(a) $|z - 1| = 1$.

(b) $|z - 1| = 2|z - 2|$.

(c) $1/z = \bar z$.

(d) $\Re(z) = 3$

(e) $\Im(z) = a$ with $a \in \mathbb{R}$.

(f) $Re(z) > a$ with $a \in \mathbb R$.

(g) $|z - 1| < 2|z - 2|$.\subsection{}
Prove that $$|z_1 + z_2 | \geq |~|z_1 | - |z_2 |~|$$ and explain when equality holds.

\subsection{}
Prove that the equation $z^3 + 2z + 4 = 0$ has its roots outside the unit circle. 

\textit{[Hint: what is the maximum value of the modulus of the first two terms if $|z| \leq 1$?]}

\subsection{}

(a) Prove that if $|w_1 | = c|w_2 |$ where c > 0, then 
$|w1- c2 w2 | = c|w1 $-$ w2 |$.
z $-$ z1| = c represents a circle. Find(b) Prove that if c $>$ 0, c 6= 1 and z1 6= z2 , then |z $-$ z2 its center and radius. 
[Hint: an easy way is to use part (a)]

5. (a) Let z, w be complex numbers, such that $\bar z w 6= 1$. 
Prove that
|

w$-$z

| $<$ 1 if |z| $<$ 1 and |w| $<$ 1,

1 $-$ w̄z

and also that
|
w$-$z

| = 1 if |z| = 1 or |w| = 1.

1 $-$ \bar w z

(b) Prove that for fixed w in the unit disk D, the mapping

F : z 7$\rightarrow$

w$-$z

1 $-$ \bar wz

satisfies the following conditions:

(i) F maps D to itself and is holomorphic.

(ii) F interchanges 0 and w, namely, F (0) = w and F (w) = 0.

(iii) |F (z)| = 1 if |z| = 1.

(iv) F : D 7$\rightarrow$ D is bijective. [Hint: Calculate F ◦ F .]

6. Use n-th roots of unity (i.e. solutions of z n $-$ 1 = 0) to show that

2n$-$1 sin

$\pi$

2$\pi$

(n $-$ 1)$\pi$

sin

· · · sin

=n.

n

n

n

\textit{
  [Hint: 1 $-$ cos 2$\theta$ = 2 sin2 $\theta$, sin 2$\theta$ = 2 sin $\theta$ cos $\theta$.]
}
1

\subsection{}
Prove that f (z) = |z|2 has a derivative only at z = 0, but nowhere else.

\subsection{}
Let f (z) be analytic in a domain. Prove that f (z) is a constant if it satisfies any of

the following conditions:

(a) |f (z)| is constant;

(b) Re(f (z)) is constant;

(c) arg(f (z)) is constant;

(d) f (z) is analytic;

How do you generalize (a) and (b)?

\subsection{}
Let f (z) be analytic. Show that f (z̄) is also analytic.

\subsection{}

(a) Show that in polar coordinates, the Cauchy-Riemann equations take the form

1 $\partial$v $\partial$v 1 $\partial$u $\partial$u= and
=$-$
$\partial$r

r $\partial$$\theta$

$\partial$r

r $\partial$$\theta$

(b) Use these equations to show that the logarithm function defined by

log z = log r + i$\theta$ where z = rei$\theta$ with $-$ $\pi$ $<$ $\theta$ $<$ $\pi$

is a holomorphic function in the region r $>$ 0, $-$$\pi$ $<$ $\theta$ $<$ $\pi$. Also show that log z

defined above is not continuous in r $>$ 0.

\subsection{}
Prove that the distinct complex numbers z1 , z2 and z3 are the vertices of an equilateral triangle if and only if
$z12 + z22 + z32 = z1 z2 + z2 z3 + z3 z1$.
